VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper.tex
add paper files
deleted old main.pdf, adjusted failures to 10 for figures
update deletion eval
as dense as I could make it
revise
revised
rev

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

\newcommand{\comments}[1]{}

@@

%\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
\title{
Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
%\author{
%  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
%  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
%}

@@

\input{fast14_abstract}
\input{fast14_introduction}
\input{fast14_background}
\input{fast14_deduplication}
\input{fast14_architecture}
\input{fast14_evaluation}
\input{fast14_conclusion}

\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{document}

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

\newcommand{\comments}[1]{}
\newcommand{\todo}[1]{\textit{\color{red}#1}}

@@

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
\title{
VM-Centric  Snapshot Deduplication  with Fault Isolation 
for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

@@

\input{paper_abs}
\input{paper_intro}
\input{paper_background}
\input{paper_dedup}
\input{paper_analysis}
\input{paper_del}
\input{paper_arch}
\input{paper_eval}
\input{paper_conc}

\begin{small}
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{small}
\end{document}

### 2014-01-31 snapshot_system/paper_del.tex
rev

\item {\bf Periodic repair of leakage}.
%[exlpain why second Bloom filter, why scan append store]
Leakage repair is conducted periodically to fix the above approximation error.
This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
A mark-and-sweep process  requires a scan of all the metadata for a snapshot store.
%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
%in a way that the data dependency is clearly known.
%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
Since it is a VM-specific procedure, 
the space and time cost is relatively small compared to the tranditional mark-and-sweep
which scans snapshot chunks from all VMs.
For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
\end{itemize}

>>>>

\item {\bf Periodic repair of leakage}.
%[exlpain why second Bloom filter, why scan append store]
Leakage repair is conducted periodically to fix the above approximation error.
This procedure compares the live chunks for each VM with what are truly used in the VM snapshot recipes.
A mark-and-sweep process  requires a scan of all the metadata for a snapshot store.
%Our VM-centric mark-and-sweep procedure is similar to Guo\cite{Guo2011} 
%in a way that the data dependency is clearly known.
%This generally requires a scan of almost the entire snapshot store which is much more expensive than approximate deletion,
%although certain optimized algorithms may apply\cite{Przemyslaw2013}. But 
Since it is a VM-specific procedure, 
the space cost for processing each VM is proportional to the number of chunks
within each VM. For example, it is about 85MB space requirement for a VM of size 40GB in our tested dataset.
 This is  much smaller compared to the tranditional mark-and-sweep
which scans snapshot chunks from all VMs. Given $n$ VMs in a cluster, the space cost
is $n$ times larger.
%For example, consider each reference consumes 8 bytes plus  1 mark bit. A VM that has 40GB backup data with about
%10 million chunks will need less than 85MB of memory to complete a VM-specific mark-and-sweep process
%in less than half an hour, assuming 50MB/s disk bandwidth is allocated.
\end{itemize}

### 2014-01-31 snapshot_system/paper_eval.tex
rev

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally.

\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Our results show that VC has a significantly  higher availability than VO as the number of
failed machines increases from 3 to 20
in this table.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 machine failures,
there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% loses data for 8 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block. Since most blocks contain chunks for a single
VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
On the other hand, when $p=1000$, the pecetnage of machine failure is then 2\% and
 VC outperforms VO significantly in availabilty in this case by delivering a meaningful avaiability with 99.62\%.

@@

%By having extra replicas for the PDS data, we reduce the failure rate of PDS
%FSBs enough that the failure rate for the VM approaches the failure rate of the
%Non-PDS blocks. This minimizes the drop in availability between the expected
%and worst case for VC.
%
%One of the advantages of VC is that there is a division between
%popular and non-popular data to facilitate improved reliability. 
Figure~\ref{fig:pds-replication} shows
the impact of increasing PDS data replication degree. 
While the impact on storage cost is small (because we have separated out only
the most popular blocks),
a replication degree of 6  has a significant improvement over 4. The
availability does not increase much  when increasing
$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
That is because when the number of failed machines increases beyond 6, 
the non-PDS data availability starts to deteroriate significantly given its replication degree
$r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings
and
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
duplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all deduplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
VM cluster in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
significantly because of the controlled  disk read bandwidth usage.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

It should be noted that global fingerprint  space requirement of VC is about 2\% of SRB 
(with $\sigma$=2\%) since we only deal with popular items. 
\comments{
The total memory space would cost over 6GB per machine.
We have implemented a bloomfilter for SRB which uses a comparable in-memory
index space size per machine compared VC, but SRB also needs extra space for caching hot index.
The total space used in SRB is about 1GB per machine. 
}

{\bf Processing Time breakdown}.
Table~\ref{tab:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

\begin{table}[t]
  \centering
    \footnotesize
    %\tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        col sep=tab,
        %columns={Algorithm,Snapshot Read/Write,Network Transfer,Index access and comparison},
        columns={Algorithm,ReadWrite,Network,Index},
        columns/Algorithm/.style={
            string type,
            column name={\multirow{2}{*}{Algorithm}}
        },
        columns/ReadWrite/.style={
            column name={
                \multicolumn{3}{c|}{Time Spent in Task (ms)}\\&
                Read/Write
            },
            multiply by={1000},
            %preproc cell content/.code={1#1 1},
            fixed, precision=3
        },
        columns/Network/.style={
            column name={Network},
            multiply by={1000},
            fixed, precision=3
        },
        columns/Index/.style={
            column name={Index Lookup},
            multiply by={1000},
            fixed, precision=3
        },
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
    ]{figures/vc_srb_combined_pgfplots.txt}
    \caption{Average time in microsecond to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
%        \todo{Decide between this and bar plot with the same caption}
    }
    \label{tab:vc_srb_combined}
\end{table}

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when when I/O throttling is not applied to control the usage.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

@@

 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}

In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
then start to delete those snapshots one by one.
As we know the actual storage needs after each snapshot creation,
the storage leakage can be detected by
comparing the size of remaining data in use after deletion to the correct number.
Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the solid line represents the actual average leakage measured during the experiment for all the VMs. 
The Bloom filter setting is based on $\Delta u/u=0.025$.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
there is only 1.5MB space leaked for every 1GB of stored data.
The actual leakage can reach  4.1\% after  245 deletions.
This experiment shows that the leakge of our approximate snapshot deletion is very small, 
below the estimated number.

>>>>

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing a data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.
\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Our results show that VC has a significantly  higher availability than VO as the number of
failed machines increases from 3 to 20
in this table.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 machine failures,
there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% loses data for 8 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block. Since most blocks contain chunks for a single
VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
On the other hand, when $p=1000$, the percentage of machine failure is then 2\% and
 VC outperforms VO significantly in availability in this case by delivering a meaningful availability with 99.62\%.

@@

%By having extra replicas for the PDS data, we reduce the failure rate of PDS
%FSBs enough that the failure rate for the VM approaches the failure rate of the
%Non-PDS blocks. This minimizes the drop in availability between the expected
%and worst case for VC.
%
%One of the advantages of VC is that there is a division between
%popular and non-popular data to facilitate improved reliability. 
Figure~\ref{fig:pds-replication} shows
the impact of increasing PDS data replication degree. 
While the impact on storage cost is small (because we have separated out only
the most popular blocks),
a replication degree of 6  has a significant improvement over 4. The
availability does not increase much  when increasing
$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
That is because when the number of failed machines increases beyond 6, 
the non-PDS data availability starts to deteriorate significantly given its replication degree
$r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings
and
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
duplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Table ~\ref{tab:resource_usage} shows that when  each machine conducts
backup one VM at a time, the backup of the entire
VM cluster completes in about 1.31 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
significantly in this case because of the controlled  disk read bandwidth usage.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

It should be noted that global fingerprint  space requirement of VC is about 2\% of all unique fingerprints 
with $\sigma$=2\%. SRB uses an approximated method to look for a match within a bin and
its memory space usage is about 190MB per machine. That is compared with 118MB used in VC with $\sigma=2\%$.
Using a bloom filter with an index cache would require more memory space~\cite{Dong2011}.

\comments{
The total memory space would cost over 6GB per machine.
We have implemented a bloom-filter for SRB which uses a comparable in-memory
index space size per machine compared VC, but SRB also needs extra space for caching hot index.
The total space used in SRB is about 1GB per machine. 
}

{\bf Processing Time breakdown without I/O throttling}.
Table~\ref{tab:vc_srb_combined} shows
the  average  processing  time of  a dirty VM segment in milliseconds
under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
The overall processing latency of SRB is about 23.9\% slower than VC.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB. 
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

\begin{table}[t]
  \centering
    \footnotesize
    %\tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        col sep=tab,
        %columns={Algorithm,Snapshot Read/Write,Network Transfer,Index access and comparison},
        columns={Algorithm,ReadWrite,Network,Index},
        columns/Algorithm/.style={
            string type,
            column name={\multirow{2}{*}{Algorithm}}
        },
        columns/ReadWrite/.style={
            column name={
                \multicolumn{3}{c|}{Time Spent in Task (ms)}\\&
                Read/Write
            },
            multiply by={1000},
            %preproc cell content/.code={1#1 1},
            fixed, precision=3
        },
        columns/Network/.style={
            column name={Network},
            multiply by={1000},
            fixed, precision=3
        },
        columns/Index/.style={
            column name={Index Lookup},
            multiply by={1000},
            fixed, precision=3
        },
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
    ]{figures/vc_srb_combined_pgfplots.txt}
    \caption{Average time in milliseconds  to backup a dirty 2MB VM segment under SRB and VC with I/O throttling.
%        \todo{Decide between this and bar plot with the same caption}
    }
    \label{tab:vc_srb_combined}
\end{table}

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when when I/O throttling is not applied to control the usage.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset, each version of total snapshots  has abut  1TB per machine for 25 VMs and  thus  each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

@@

\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
\end{small}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

Table~\ref{tab:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
then start to delete those snapshots one by one.
As we know the actual storage needs after each snapshot creation,
the storage leakage can be detected by
comparing the size of remaining data in use after deletion to the correct number.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the solid line represents the actual average leakage measured during the experiment for all the VMs. 
The Bloom filter setting is based on $\Delta u/u=0.025$.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
there is only 1.5MB space leaked for every 1GB of stored data.
The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
to the  leakage under 5\%. 
This experiment shows that the leakage of our approximate snapshot deletion is very small, 
below the estimated number.

The space cost for deletion and leakage repair is very small.
Consider each reference consumes 8 bytes plus  1 mark bit. 
A VM that has 40GB backup data with about 10 million chunks will need less than 85MB of memory.
A VM-specific mark-and-sweep process takes  less than half an hour, when disk bandwidth is controlled as 50MB/s.

When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, a total of 212GB memory
space on 100 node is accessed for processing each VM and each machine quires 2.12GB.
Assuming snapshot deletion happens daily,
such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
since there is 2.5\% data change for each snapshot.
